Networked Character Devices

### 2011-12-12 report/paper.tex
Added intro and related work

\newenvironment{packed_item}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}}

@@

@@

@@

We are unique.

@@

% vim: set ts=2 sts=2 sw=2 et spell tw=72 : %

>>>>

\newenvironment{packed_item}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
\label{sec:introduction}

}{\end{itemize}}

@@

We have designed and implemented Network Character Devices (NCD) to
enable a new approach to using and sharing devices. Today, networking 
technology is becoming faster and more reliable at incedible rates. 
More functionality that has been traditionally thought to only be 
feasabily locally accessable can now be pushed to remote
machines. Using client-server operation, our project aims to allow 
a character device (or devices) present on a server to be exported to
a client over a network connection. While character devices come in 
many forms, from Webcams, mice and monitors to USB flash drives and 
external hard drives, NCD works below where these devices are 
interpreted and exports their device file over IP. While designed for
character devices, this generality will actually allow us to export 
any file, which in a *nix system means almost anything on the
system. Being able to dynamically export devices over network
connections suggests a new cloud-like paradigm of device usage where 
locality is required only for reduced latency, which may not be a
concern for certain devices.

When a device is being exported by NCD we would like it to give the
appearence of having essentially ``moved'' the device to the client 
by forbidding user level accesses on the server. This is not part 
of our current iteration of NCD, but it will be included as higher
level functionality is implemented. Aquiring a remote device will be
done through an advertisment protocol that exists in user space so
that details may be supplied about the server and how the connection
should be made (e.g. UDP vs TCP).  After this NCD's functionality on
the client exists in kernel space so as to maintain transparency to
user level operations. Once imported, a device should be accessed just
like a normal local device.  This is acheived by the NCD kernel module
intercepting accesses and sending them out over the network to the
server. On the server, a userspace daemon accesses the physical
device to emulate the client's activity. The overall structure of the
NCD system is present in figure 1.

@@

Currently we have achieved a successful implementation of the low
level functionality for NCD. The client uses a kernel module written
for linux 2.6.x+ while the server uses a userspace daemon. NCD is
still rough and in need of further development, as it tends to be
crash prone if not treated with care. The groundwork has been laid for
exporting any device, however many device subsystems access their
devices by avoiding the character device interface and these must be
dealt with on an individual basis. Overall, the path for future work
is very clear.

@@

There are many other projects in existence that implement similar
network sharing in one form or another that provided inspiration for
NCD.

NFS was the first implementation of truely general information sharing
over remote network connections.  However, NFS uses a specific file
system and cannot interface directly with devices.\cite{nfs-source}

NBD (Network Block Device) was included into the linux kernel starting
with version 2.1.101. It enables users to export block devices over the
network, allowing use of any filesystem. However, NBD provides no
exclusive access guarantees and users must acertain on their own
whether the remote drive is being used.\cite{nbd-source}

CUSE (Character Device in User Space) is an extension of FUSE that
allows bringing a characer device into a FUSE filesystem.  This allows
users to access the device directly and potentially export it using
user-level networking.\cite{cuse-article}

USB/IP is a project to share USB devices over IP. This project is
very similar to NCD (as USB devices are character devices) but is
tailored specifinterceptingically to allow sharing USB devices over a
network connection by intercepting USB specific data and encapsulating
it in IP.\cite{usbip-source}

Plan 9 is a distributed operating system developed as a successor to
Unix by Bell Labs.  It implicitly allows sharing devices over a
network via file interfaces. However, plan 9 does not currenty see
wide deployment.\cite{plan9-pike}

@@

% vim: set ts=2 sts=2 sw=2 et spell tw=72 : %
intercepting
